---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Problem 2 

Look at NYC restaurants data 

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


## Load Instacart dataset.

```{r load_data, include = FALSE}
data("rest_inspec")

nyc_rest_inspec = 
  rest_inspec %>% 
  sample_n(5000) %>% 
  select(action, boro, cuisine_description, inspection_date, inspection_type, dba, score, grade, critical_flag) %>% 
  filter(inspection_type == "Cycle Inspection / Re-inspection") %>% 
  drop_na(score, grade)
```

# Plots

## Scatterplots

```{r}
nyc_rest_inspec %>% 
  mutate(text_label = str_c("\nGrade: ", grade, "\nBorough: ", boro)) %>% 
  plot_ly(
    x = ~inspection_date, y = ~score, type = "scatter", mode = "markers",
    color = ~boro, text = ~text_label, alpha = 0.5)
```

The trend over time for restaurant scores pretty consistent. Most of the restaurants get an A grade. Restaurants in queens and brooklyn seem to have a lower score than the rest of the boroughs.

## boxplot

```{r}
nyc_rest_inspec %>% 
mutate(cuisine_description = fct_reorder(cuisine_description, score)) %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box", colors = "viridis")
```

Pancakes/waffles and german cuisines tend to have lower ratings compared to Amercian and Asian cuisines. 

## Barplot 

```{r}
nyc_rest_inspec %>% 
  count(boro, critical_flag) %>% 
  mutate(boro = fct_reorder(boro, n)) %>% 
  plot_ly(x = ~boro, y = ~n, color = ~critical_flag, type = "bar", colors = "viridis")
```

The number of critical violotaions are greater than non-critical violotions among all the boroughs.


